\documentclass[10pt, letterpaper]{article}

\usepackage[top=1.6cm, bottom=1.6cm, left=1.7cm, right=1.7cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=black]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{2pt}\titlerule]
\titlespacing{\section}{0pt}{0.35cm}{0.2cm}

\begin{document}

\begin{center}
    {\fontsize{22pt}{22pt}\selectfont \textbf{Shridhar}} \\
    \vspace{6pt}
    {\large \textbf{Software Engineer}} \\
    \vspace{8pt}
    Bangalore, India | \href{mailto:john@example.com}{john@example.com} | 9838923892 \\
    \vspace{2pt}
    \href{LinkedIn: linkedin.com/in/shridharsharma | GitHub: github.com/shridharsharma}{LinkedIn} \quad | \quad \href{https://github.com/rahulverma}{GitHub} \quad | \quad \href{https://www.linkedin.com/in/rahul-verma-dev}{Portfolio}
\end{center}

\section{Summary}
Results-driven AI and web developer with expertise in software engineering and data analysis.

\section{Technical Skills}
Programming: Python, Java, JavaScript, React, FastAPI, Django \\
Cloud Computing: AWS, Docker, Kubernetes \\
Database Management: PostgreSQL, Redis \\
Version Control: Git, CI/CD \\
Operating System: Linux

\section{Experience}
\textbf{Software Engineer Intern} -- Google \hfill January 2020 - Present \\
\begin{itemize}
\item Designed and implemented API integrations, resulting in a 30\% reduction in deployment time.
\item Optimized database query latency by 25\%, improving overall system performance.
\end{itemize}


\section{Projects}
\textbf{AI Resume Builder} \hfill 2026 \\
\begin{itemize}
\item Utilized Python, Streamlit, and Groq to develop a user-friendly AI-powered resume builder.
\item Deployed the application on Render, ensuring seamless scalability and reliability.
\item Created an attractive and intuitive UI, resulting in a 95\% user satisfaction rate.
\end{itemize}
\textbf{Crypto Portfolio Tracker} \hfill March 2025 \\
\begin{itemize}
\item Developed a portfolio calculator using the CoinLore API, reducing calculation time by 50\%.
\item Implemented rate limiting using caching, ensuring a 99.9\% uptime rate.
\item Designed an easy-to-use UI, resulting in a 90\% user adoption rate.
\end{itemize}


\section{Education}
\textbf{B.Tech in CSE} -- IITD, Delhi \hfill 2023-2027 \\ GPA: 9/10 \\
\vspace{4pt}
\textbf{Class XII (CBSE)} -- DPS \hfill 2022 \\ Percentage: 90 \\
\vspace{4pt}
\textbf{Class X (CBSE)} -- DPS \hfill 2020 \\ Percentage: 90

\section{Certificates}
\href{https://dashboard.render.com/web/srv-d5n64o5actks73c9n4lg/deploys/dep-d5n64olactks73c9n4u0}{AWS cloud} \\


\end{document}